---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LSMS - RStudio Project Template 1: Technical Reports

## Background

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This is a preliminary version of a template for LSMS technical reports (i.e. sampling reports, data preparation reports). It is based on the [Rstudio project template](https://rstudio.github.io/rstudio-extensions/rstudio_project_templates.html). The main aim of this (and similar templates) is the standardization of the report creation process, and the increase in reproducibility, in line with the World Bank's reproducible research principles. For more details on the World Bank's approach to reproducible research, please see [here](https://reproducibility.worldbank.org/index.php/home).


## Project set-up

After installing the package, you can create a new project from the template by selecting "File > New Project > New Directory > LSMS report template" in Rstudio. You will be asked to provide a project name and a directory where the project should be created. The project will be created in a new directory with the name you provided. The project directory will contain the following files and directories:


```{r, eval=FALSE, echo=TRUE}
├── data
│   ├── in
│   └── out
├── doc
├── R
│   └── report_data_preparation.R
├── myproject.Rproj
├── templates
│   └── word
│       ├── logoWBDG.png
│       └── report_template_DECLS_v2.docx
└── text
    ├── sec1_para1.txt
    ├── sec1_para2.txt
    ├── sec2_para1.txt
    ├── sec3_para1.txt
    ├── sec3_para2.txt
    └── sec3_para3.txt
    
```

The package itself is based on the [officer](https://davidgohel.github.io/officer/) package and contains only one main function (plus a few helpers) to create a Word document from a template, this template can also be replaced. During the creation of the project, the word template is copied to the templates directory. 

The main function is called `genreport()` and requires one main input, which is the list of word document elements. The file `R/report_data_preparation.R` contains an example set up script, which can be modified to fit the needs of the report. The function `genreport()` is called at the end of the file and will create the Word document in the `doc` directory.

In the `text` directory, you can place the text elements used in the report. During the project creation process, some example files are created in line with the names used for the different input list elements written in the `R/report_data_preparation.R` file.

The `doc` directory contains the final report, which is created by the `genreport()` function. The `data` directory contains two subdirectories, `in` and `out`. The `in` directory is used to store the input data, the `out` directory is used to store the output data. The `R` directory contains the `report_data_preparation.R` file, which is used to create the report. The `myproject.Rproj` file is the Rstudio project file.

In addition the template also creates a local **.Rprofile**, with the following content:

```{r, eval=FALSE, echo=TRUE}
# .Rprofile
library("lsmsrprojtempl1")

```

This will load the package automatically when the project is opened.

**ATTENTION:** This package is at an early stage of development and will be updated regularly. Please check for updates regularly, and if you have any suggestions or comments, please let me know. One of the next steps will also be the addition of a Power Point template, currently only the word template is available. In addition the Github option, even though available during the project creation process, is not yet fully functional.



## Installation

* Install R: https://cran.r-project.org/mirrors.html (version 4.1.1 or greater)

* Install R Studio: https://rstudio.com/products/rstudio/download/ (version 1.2.5001-3 or newer)

* Make sure the *devtools* package is installed, if not install it with:

```{r devtoolsinst,eval=FALSE, echo=TRUE}
install.packages("devtools")

```


* After that install the actual package:

```{r install,eval=FALSE, echo=TRUE}
devtools::install_github("michael-cw/lsmsrprojtempl1")

```
